---
title: "Transmission of Useless Culture"
author: "Nicolas Restrepo"
date: "September 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

library(tidyverse)
library(igraph)
```

## First attempt

Here, I will give a first go to the agent-based model I want to run 

## Set-up 

### Environment 

Let's think about the setup. The first thing that I need to figure out is the environment. It is going to be a small world network which is easily generated with igraph. Let's begin with 30 nodes.

```{r}

# Create small world network 

sw_network <- sample_smallworld(dim = 1, size = 30, nei = 2, p = 0.1, 10, loops = F)

# Visualize it 

plot(sw_network, vertex.size = 6, vertex.label = NA, layout = layout_in_circle)

```

Now that we have the igraph object I can extract the matrix of nodes

```{r}

# Extract network matrix 

net_matrix <- as.matrix(sw_network[])

```

### Agents 

Let's say that we will keep track of each agent using a dataframe. Each agent will have different columns for each pereference as well as for their overall conviction score.  

```{r}

# Create empty dataframe for the weights of preferences

data <- tibble(agent = 1:30, 
               h1 = 1, 
               h2 = 1, 
               h3 = 1, 
               h4 = 1)

```

I think this will do for now. 

Now let me think about how actual updating might seem like. Let's go step by step. The first step would be to decide how the distributions of each preference get established. 

```{r}
values <- tibble(rw = rnorm(0, 1, n = 1000),
                 w4 = rnorm(1, 1, n = 1000), 
                 w2 = rnorm(1.25, 1, n = 1000), 
                 w3 = rnorm(1.5, 1, n = 1000), 
                 w1 = rnorm(1.75, 1, n = 1000)) %>% 
  gather()

values %>% 
  ggplot(aes(x = value, color = key)) + 
  geom_density(aes(fill = key ), alpha = 0.3)

```

Alright let's try with these distributions to begin with. 


### Procedure 

I need to begin thinking about the process itself. The first step here is to think about which representation is each agent going to play at the beginning of each turn. Let me conceive of it as a series of little procedures and then I can turn it into a more reproducible function. 

```{r}


go <- function(x) {

# Draw from each distribution according to the weight of each actor 

w1 <- rnorm(0.25, 1, n = data$h1[x])

w2 <- rnorm(0.5, 1, n = data$h2[x])

w3 <- rnorm(0.75, 1, n = data$h3[x])

w4 <- rnorm(1, 1, n = data$h4[x])

# Concatenate all values into a dataframe

draws <- data.frame(w1, w2, w3, w4) %>% gather()

# Which distribution produced the draw closest to zero 

lowest <- draws %>% 
  mutate(value = abs(value)) %>% 
  filter(value == min(value))

played <- lowest$key

 
}

# Create vector of heuristics played on first round 

disp <-  map_chr(c(1:30), go)
```

Now I should try to find out my agents neighbor

```{r}

for (i in 1:30) {
  
# Find the neighbors of my agent

neighbors <- which(net_matrix[i,] != 0)

# Dispositions that should be updated

to_update <- disp[neighbors]

w_w1 <- sum(str_detect("w1", to_update))

w_w2 <- sum(str_detect("w2", to_update))

w_w3 <- sum(str_detect("w3", to_update))

w_w4 <- sum(str_detect("w4", to_update))

# Update the weights on the original dataframe 

data$h1[i] <- data$h1[i] + w_w1
data$h2[i] <- data$h2[i] + w_w2
data$h3[i] <- data$h3[i] + w_w3 
data$h4[i] <- data$h4[i] + w_w4

}  
  

```


Alright this is a great place. 


### Visualizing convictions 

```{r}

# Create column for the current conviction of each agent or whether they are undecided 

d_graph <- data %>% 
  mutate(conviction = case_when(h1 > h2 & h1 > h3 & h1 > h4 ~ "h1", 
                                h2 > h1 & h2 > h3 & h2 > h4 ~ "h2", 
                                h3 > h1 & h3 > h2 & h3 > h4 ~ "h3", 
                                h4 > h1 & h4 > h2 & h4 > h3 ~ "h4", 
                                h1 == h2 | h1 == h3 | h1 == h4 | h2 == h3 | h2 == 4 | h3 == h4 ~ "undecided"))


# Add convictions to the network 

V(sw_network)$conviction <- d_graph$conviction



V(sw_network)$color <- ifelse(V(sw_network)$conviction == "h1", "#117ed3", 
                              ifelse(V(sw_network)$conviction == "h2", "#d3116c", 
                                     ifelse(V(sw_network)$conviction == "h3", "#1e9231", 
                                            ifelse(V(sw_network)$conviction == "h4", "#d13010", 
                                                   ifelse(V(sw_network)$conviction == "undecided", "#7412c7", "NA")))))




plot(sw_network, vertex.color = V(sw_network)$color, col="#777777", vertex.label=V(sw_network)$conviction)
```

Awesome! You have a plot where certain heuristics are flowing. 

### Making it iterative 

Here, I am going to start making the first loop 


```{r}

after_each_round <- matrix(0, 30, 5)

for (k in 1:5) {
  
  disp <- matrix(0, 30)
  
  for (i in 1:30) {
    
    # Draw from each distribution according to the weight of each actor 
    
    w1 <- rnorm(-4, 1, n = data$h1[i])
    
    w2 <- rnorm(4, 5, n = data$h2[i])
    
    w3 <- rnorm(-3, 5, n = data$h3[i])
    
    w4 <- rnorm(3, 1, n = data$h4[i])
    
  
    # Concatenate all values into a list
    
    draw_list <- list("w1" = w1, 
                      "w2" = w2, 
                      "w3" = w3, 
                      "w4" = w4)
    
    # Take the absolute value of each draw
    
    absolute_draws <- map(draw_list, abs)
    
    # What is the minimum? 
    
    draws <- map_dbl(absolute_draws, min)
    
    # add that to the dispositions 
    
    disp[i, ] <-names(which.min(draws))
    
  }
  
  for (j in 1:30) {
    
    
    # Find the neighbors of my agent
    
    neighbors <- which(net_matrix[j,] != 0)
    
    # Dispositions that should be updated
    
    to_update <- disp[neighbors]
    
    w_w1 <- sum(str_detect("w1", to_update))
    
    w_w2 <- sum(str_detect("w2", to_update))
    
    w_w3 <- sum(str_detect("w3", to_update))
    
    w_w4 <- sum(str_detect("w4", to_update))
    
    # Update the weights on the original dataframe 
    
    data$h1[j] <- data$h1[j] + w_w1
    data$h2[j] <- data$h2[j] + w_w2
    data$h3[j] <- data$h3[j] + w_w3 
    data$h4[j] <- data$h4[j] + w_w4
    
  }  
  
  d_graph <- data %>% 
    mutate(conviction = case_when(h1 > h2 & h1 > h3 & h1 > h4 ~ "h1", 
                                  h2 > h1 & h2 > h3 & h2 > h4 ~ "h2", 
                                  h3 > h1 & h3 > h2 & h3 > h4 ~ "h3", 
                                  h4 > h1 & h4 > h2 & h4 > h3 ~ "h4", 
                                  h1 == h2 | h1 == h3 | h1 == h4 | h2 == h3 | h2 == 4 | h3 == h4 ~ "undecided"))
  
  
  after_each_round[, k] <- d_graph$conviction
  
  if (k %% 1) { 
    
    V(sw_network)$conviction <- d_graph$conviction
    
    
    
    V(sw_network)$color <- ifelse(V(sw_network)$conviction == "h1", "#117ed3", 
                                  ifelse(V(sw_network)$conviction == "h2", "#d3116c", 
                                         ifelse(V(sw_network)$conviction == "h3", "#1e9231", 
                                                ifelse(V(sw_network)$conviction == "h4", "#d13010", 
                                                       ifelse(V(sw_network)$conviction == "undecided", "#7412c7", "NA")))))
    
    
    
    
    plot(sw_network, vertex.color = V(sw_network)$color, col="#777777", vertex.label=V(sw_network)$conviction)
    }
}
```

